%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
% \renewcommand\tabularxcolumn[1]{m{#1}} % vertically center tabularx elements

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.4\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\colorbox{black}{{\Huge\textcolor{white}{\textbf{\MakeUppercase{Preston Walraven}}}}} % First name
	% \colorbox{black}{{\Huge\textcolor{white}{\textbf{\MakeUppercase{Walraven}}}}} % Last name
	
	\vspace{6pt}

	{\LARGE \textbf{Software/Computer Engineer}} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.26\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% \icon{MapMarker}{12}{Golden, CO}\\
	\icon{Phone}{12}{720-339-7703 (cell)}\\
	\icon{EnvelopeO}{12}{\href{mailto:prestoni1@comcast.net}{prestoni1@comcast.net}}\\	
\end{minipage}
\begin{minipage}[t]{0.34\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\icon{Github}{12}{\href{https://github.com/PrestonWalraven}{github.com/PrestonWalraven}}\\
	\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/prestonwalraven/}{linkedin.com/in/prestonwalraven}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

I am an engaged and versatile computer scientist with a strong foundation in math, logic, 
and problem solving. I take pride in my technical abilities - but also in my effective 
communication, organization, and my propensity to develop lasting relationships with both coworkers
and clients.

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\begin{table}[h!]
	\begin{tabularx}{\textwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
		\hline
		\textbf{Category} & \textbf{Some Experience} & \textbf{Proficient} & \textbf{Adept} \\ 
		\hline
		\textbf{Languages} & C\#, Rust, OCaml, MIPS, Verilog HDL & JavaScript, HTML, CSS, R & C, C++, Python, Java, SQL, Bash \\ 
		\hline 
		\textbf{Frameworks, Platforms, Libraries} & Tensorflow, Matplotlib, Docker, Unity & RTOS, scikit-learn, AWS, Ceedling, GTest, JUnit & Numpy, Linux, WSL \\
		\hline
		\textbf{Development Processes, Tools} & Waterfall, Continuous Integration & Test Driven Development, Doxygen & Agile, Scrum, Unit Testing, Git \\
		\hline
		\textbf{Knowledge Areas} & Discrete Math, Digital Logic, Operating Systems & Probability, Stats, LinAlg, Deep \& Classical ML, Info Security & Embedded Systems, Computer Networks, OOP \\
		\hline
	\end{tabularx}
\end{table}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry % Lead TA Fall 2021 and Spring 2022
		{8/2021 -- Present\\\footnotesize{part time}}
		{Lead Teaching Assistant - Data Structures}
		{Colorado School of Mines}
		{Coordinated a team of 11 TAs for grading and class support efforts. Interfaced with the instructors to 
		contribute to course direction decisions and to keep the course material up to date. Provided support 
		for 250+ students through office hours, in-class lab guidance, and grading feedback.}
	\entry % Imaged Reality Fall 2021
		{8/2021 -- 12/2021\\\footnotesize{part time}}
		{Software Engineer}
		{Imaged Reality}
		{Client Liaison and Group Leader for CS Field Session. Guided a team of 4 peers to develop plugin functionality for 3DGaia, 
		a 3D platform for geoscience collaboration and education in virtual reality. Worked in Unity to accommodate geodetic file types, 
		perform coordinate conversion calculations applied to meshes, and add user facing features to integrate geological tools into 
		the product.}
	\entry % Syncroness Summer 2021
		{6/2021 -- 8/2021}
		{Software Engineering Intern}
		{Syncroness}
		{Continued development on the visitor check-in notification system that leverages AWS, focusing on real world
		customer usage and product reliability. Performed unit, system, and user testing to ensure quality.}
	\entry % TA Spring 2021
		{1/2021 -- 5/2021\\\footnotesize{part time}}
		{Teaching Assistant - Data Structures}
		{Colorado School of Mines}
		{Guided students in office hours and in-class labs, gathered valuable feedback for improving the course, and 
		provided support for struggling students through tutoring.}
	\entry % Syncroness Summer 2020
		{6/2020 -- 8/2020}
		{Software Engineering Intern}
		{Syncroness}
		{Ensured software quality by creating and updating unit tests for an Embedded C device.
		Migrated and archived old code repositories to reduce clutter and storage costs.
		Piloted development on a visitor check-in notification system that leverages AWS IoT, Lambda, DynamoDB, and SES.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2019 -- Present}
		{BS in Computer Science - Computer Engineering}
		{Colorado School of Mines}
		{\begin{itemize}[noitemsep, topsep=0pt]
			\item 4.0 GPA, Dean's List every semester
			\item Accepted into the CS Grad Program.
			\item Focus areas in Embedded Systems, Machine Learning, and Data Structures.
			\item Thorson Honors Student
		\end{itemize}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{English} - native\\
	\textbf{Spanish} - proficient
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	Camping, Fishing, Making Music, Building Guitar Pedals, Biking.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Achievements}
	
	Boy Scouts of America Eagle Scout
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
